Molecular dynamics simulation of synchronization in driven particles

### 2021-01-30 manuscript/manuscript_ajp_2020.tex
described Brownian figure

%\item
  \subsection{Integration Methods}
    \label{ex:euler}
    To calculate the position of the particle we
    integrate the equation of motion using
    the standard definition of velocity
    $\vec{v}_i = d\vec{r}_i/dt$ 
    via the 
    %In our model we use the
    Euler method. % to solve this equation.
    Our equation of motion provides
    a direct calculation for particle velocity,
    as demonstrated in Ex.~\ref{ex:n2l}.

@@

%\item
  \subsection{Brownian motion}
  \label{ex:brownian}
  Brownian motion 
  is a temperature and viscosity dependent
  phenomena.
  Particles change direction %randomly
  due to collisions with fluid particles.
  The frequency of collisions depends on the properties of
  the suspending fluid.
  These collisions are more likely at higher temperature
  due to the increased kinetic energy of the fluid particles,
  as described by the Maxwell-Boltzmann distribution \cite{Einstein1905}.

@@

  % (a) 
  In simulation we define our temperature parameter to
  $k_b T/E_0 \rightarrow T$
  since we set the constants to unity.
  In these units we can compare 
  simulation temperature directly
  to force 
  in order to estimate the degree of random fluctuation.
  For instance, 
  with
  no applied driving force,
  the minimum temperature required for a single particle
  to hop between minima in the potential landscape is
  $T_{min} > A_p$.
  Assuming a particle is confined to
  move along the $y-$direction,
  include Brownian motion 
  in the model.
  Measure the position vs. time
  of a non-driven colloid for $T/A_p = 4.0, 5.0, 6.0$
  and note  a particle will hop a barrier
  for sufficiently high $T/A_p$ ratios.
  We find the crossover
  to a hopping regime at $T/A_p \approx 5.6$
  %when
  \begin{center}
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{{brownian_particle_dt0.1}.pdf}
      \caption{
        Motion of a particle undergoing Brownian motion
        on a washboard potential
        energy landscape.
        (a) $T/A_p = 4.0$ no hopping occurs.
        (b) $T/A_p = 5.0$ a single hop occurs at $t = 130000$
        (c) $T/A_p = 6.0$ many hops occur.
        Note the scale of the $y-$axis differs in each panel.
      }
      \label{fig:brownian}
    \end{figure}
  \end{center}
  In Fig.~\ref{fig:brownian}

>>>>

%\item
  \subsection{Integration Methods}
  \label{ex:euler}
  %{\it cut this one?  not really saying much}
    To calculate the position of the particle we
    integrate the equation of motion using
    the standard definition of velocity
    $\vec{v}_i = d\vec{r}_i/dt$ 
    via the 
    %In our model we use the
    Euler method. % to solve this equation.
    Our equation of motion provides
    a direct calculation for particle velocity,
    as demonstrated in Ex.~\ref{ex:n2l}.

@@

%\item
  \subsection{Brownian motion}
  \label{ex:brownian}
  Brownian motion 
  is a temperature and viscosity dependent
  phenomena in which 
  particles change direction %randomly
  due to collisions with fluid particles.
  The frequency of collisions depends on the properties of
  the suspending fluid.
  These collisions are more likely at higher temperature
  due to the increased kinetic energy of the fluid particles,
  as described by the Maxwell-Boltzmann distribution \cite{Einstein1905}.

@@

  % (a) 
  In simulation we define our temperature parameter to
  $k_b T/E_0 \rightarrow T$
  since we set the constants to unity.
  In these units we can compare 
  simulation temperature directly
  to force 
  in order to estimate the degree of random fluctuation.
  For instance, 
  with
  no applied driving force,
  the minimum temperature required for a single particle
  to hop between minima in the potential landscape is
  $T_{min} > A_p$.
  Assuming a particle is confined to
  move along the $y-$direction,
  include Brownian motion 
  in the model,
  we find the crossover
  to a hopping regime at $T/A_p \approx 5.6$.
  %when
  We demonstrate this hopping
  pattern in 
  %Measure the position vs. time
  a non-driven colloid for $T/A_p = 4.0, 5.0, 6.0$.
  %and note  a particle will hop a barrier
  %for sufficiently high $T/A_p$ ratios.
  Reproduce these results.

  \begin{center}
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{{brownian_particle_dt0.1}.pdf}
      \caption{
        Motion of a particle undergoing Brownian motion
        on a washboard potential
        energy landscape.
        (a) $T/A_p = 4.0$ no hopping occurs.
        (b) $T/A_p = 5.0$ a single hop occurs at $t = 130000$
        (c) $T/A_p = 6.0$ many hops occur.
        Note the scale of the $y-$axis differs in each panel.
      }
      \label{fig:brownian}
    \end{figure}
  \end{center}
  In Fig.~\ref{fig:brownian}
  we show the position versus time of a simple particle
  confined to a sinusoidal landscape
  undergoing Brownian motion.
  We increase the temperature relative
  to the amplitude of the landscape
  troughs until the particle enters a hopping regime.
  In  Fig.~\ref{fig:brownian}(a)
  $T/A_p = 4.0$ and the particle executes a 
  random walk centered at the potential minima $y/\lambda = 10$.
  We ran many simulations and never observed a hop to another minima.
  In  Fig.~\ref{fig:brownian}(b)
  $T/A_p = 5.0$ where hops between
  potential minima are possible but not probable,
  a single hop occurs from
  $y/\lambda = 10$ to $y/\lambda = 11$ at
  $t \sim 13000 \tau$.
  In other simulations with identical parameters,
  we sometimes observed no hops or two hops between minima,
  as expected with random fluctuating systems.
  In  Fig.~\ref{fig:brownian}(c)
  $T/A_p = 6.0$ 
  we observe approximately 15 hops,
  indicating the random thermalized kicks are
  sufficiently large to make the particle perform
  a random walk of hops a top the substrate
  in addition to the small scale random walk executed
  by all particles in this section.
